Plug-and-play dual-tree algorithm runtime analysis

### 2015-10-07 bounds-files/general-runtime-bound.tex
Discuss why query and reference scale closeness is useful.

>>>>

Keeping the query and reference scales close is both beneficial for the later
theory and intuitively reasonable: recursing too quickly in the either the query
or reference node will unnecessarily duplicate work.  Suppose we recurse many
levels down the query tree before recursing down the reference tree, giving us a
set of query nodes we are considering.  For {\it each} of these query nodes, we
will then need to descend the reference tree.  Because these query nodes are
close together (with respect to the reference nodes we are considering, which
are of larger scale and thus further apart), the pruning decisions at each level
of recursion are likely to be the same for each query node.  Therefore,
recursing too far in the query tree may cause a large amount of duplicated work.
The symmetric argument applies for recursing too far in the reference tree
before recursing in the query tree.  This justifies the approach of keeping the
query and reference scales approximately equal.
